Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-29 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:29	22:46:48	(Sat29.Aug)

\begin{itemize}
\item \emph{Window function}. \Fig{mvdr_selected_windows} show frequency responses of typical windows chosen by MVDR in shadow, speckle and highlight regions in an image. The responses tend to be symmetric, minimally steered and have slightly varying mainlobe width and sidelobe suppression. We use Kaiser windows to mimic these responses.
\item \emph{Window parameters}. The Kaiser window parameter $\beta$ adjusts the compromise between resolution and sidelobe suppression. At $\beta=0$ it yields a rectangular window, and at and $\phi$ controls the amount of steering.. $\beta=0$ ) and a gaussian curve (
\end{itemize}

@@

Assuming that a robust MVDR computes the optimal windows in the minimum variance sense, it makes sense to study them. For this we selected a scene of the oil tanker wreck Holmengraa, which lies at a slanted seabed at nearly 100m\;depth. A sectorscan image of a single ping of data collected by the HISAS1030 syntetic aperture sonar is shown in \Fig{mvdr_selected_windows}, along with the window responses MVDR typically chooses in shadow, speckle and highlight regions in this image. A fairly agressive yet stable set of parameters for MVDR where used; subarray size $L=16$, temporal averaging of $K=1$, and $d=1\%$ of diagonal loading.

@@

>>>>

\begin{itemize}
\item \emph{Window type}. \Fig{mvdr_selected_windows} show frequency responses of typical windows chosen by MVDR in shadow, speckle and highlight regions in an image. The responses tend to be symmetric, minimally steered and have slightly varying mainlobe width and sidelobe suppression. We use Kaiser windows to mimic these responses.
\item \emph{Window parameter boundaries}. The Kaiser window parameter $\beta$ adjusts the compromise between resolution and sidelobe suppression. At $\beta=0$ it yields a rectangular window, and at and $\phi$ controls the amount of steering.. $\beta=0$ ) and a gaussian curve (
\item \emph{Window database size}.
\item \emph{Performance}.
\item \emph{Oversampling need}.
\end{itemize}

@@

Assuming that a robust MVDR computes the optimal windows in the minimum variance sense, it makes sense to study them. For this we selected a scene of the oil tanker wreck Holmengraa, which lies at a slanted seabed at nearly 100\;m depth. A sectorscan image of a single ping of data collected by the HISAS1030 syntetic aperture sonar is shown in \Fig{mvdr_selected_windows}, along with the window responses MVDR typically chooses in shadow, speckle and highlight regions in this image. A fairly agressive yet stable set of parameters for MVDR where used; subarray size $L=16$, temporal averaging of $K=1$, and $d=1\%$ of diagonal loading.

@@

Kaiser
Unlike the method described by Synne\aa{}g~\cite{Synnevag2008} we do not let LCA choose from  inverted Kaiser windows. These have a spatial response with mainlobe width narrower than that of a rectangular window, but at the expense of drastically increased white noise gain. We have found that these windows hardly ever get used on experimental data, in particular steered versions which ever worsened white noise gain. We can infer the same from \Fig{mvdr_selected_windows} by noting that the maximum sidelobe level rarely exceeds the rectangular window level of -13\;dB.
